\section{Overall Agent Architecture}
Agent v2.0 is built on the \textbf{Orchestrator + Direct Routing} model. Instead of a general-purpose loop, Gemini 2.5 Flash acts as the Orchestrator: classifying intent, resolving slots, executing a deterministic search route, and synthesizing results in 1--2 LLM calls.

The 5-step processing flow:
\begin{enumerate}
    \item \textbf{Intent Classification} --- Classify user intent
    \item \textbf{Clarification Gate} --- Ask for clarification if ambiguous
    \item \textbf{Memory Agent} --- Load user preferences from PostgreSQL
    \item \textbf{Route \& Execute} --- Deterministic routing to the correct search path (0 LLM calls)
    \item \textbf{LLM Synthesis} --- Generate a natural language response
\end{enumerate}

\begin{figure}[H]
\centering
\resizebox{0.55\textwidth}{!}{%
\begin{tikzpicture}[
    node distance=1.5cm and 1.5cm,
    process/.style={rectangle, draw=darkgreen, fill=darkgreen!10, rounded corners, text width=3.5cm, text centered, minimum height=1.2cm},
    decision/.style={diamond, draw=red!80!black, fill=red!10, text width=2.2cm, text centered, inner sep=0pt},
    db/.style={cylinder, draw=orange, fill=orange!20, shape border rotate=90, aspect=0.25, text width=2.5cm, text centered, minimum height=1.5cm},
    input/.style={rectangle, draw=blue, fill=blue!10, rounded corners, text width=3cm, text centered, minimum height=1cm},
    arrow/.style={thick,->,>=stealth}
]

% Nodes
\node[input] (query) {User Query};
\node[process, below=of query] (intent) {Step 1: Intent Classification (LLM)};
\node[db, right=of intent] (ttl) {TTLCache\\(Ranked Slots)};

\node[decision, below=of intent] (gate) {Step 2: Gate\\Score $\geq$ 0.75?};
\node[input, right=2.5cm of gate] (clarify) {Clarification Question (0 LLM calls)};

\node[process, below=of gate] (memory) {Step 3: Memory Agent};
\node[db, right=of memory] (pg) {PostgreSQL\\(User DB)};

\node[process, below=of memory] (route) {Step 4: Route \& Execute Search (Hybrid)};
\node[process, below=of route] (synth) {Step 5: LLM Synthesis};
\node[input, below=of synth] (output) {Final Response};

% Arrows
\draw[arrow] (query) -- (intent);
\draw[arrow, <->, dashed] (intent) -- (ttl) node[midway, above, text width=2cm, align=center, font=\scriptsize] {Merge slots};
\draw[arrow] (intent) -- (gate);
\draw[arrow] (gate) -- node[above] {No} (clarify);
\draw[arrow] (gate) -- node[right] {Yes} (memory);
\draw[arrow, <->, dashed] (memory) -- (pg) node[midway, above, font=\scriptsize] {Load ctx};
\draw[arrow] (memory) -- (route);
\draw[arrow] (route) -- (synth);
\draw[arrow] (synth) -- (output);

\end{tikzpicture}
}% end resizebox
\caption{End-to-End Workflow Diagram of Fashion Agent v2.0}
\label{fig:workflow_v2}
\end{figure}

\section{Step 1 --- Intent Classification (Router)}

\begin{tcolorbox}[title=Method: LLM Few-shot Intent Classification]
Gemini classifies queries into \textbf{7 intent groups} with a confidence score. If confidence $< 0.6$, the agent switches to the clarification step instead of searching immediately.
\end{tcolorbox}

\begin{table}[H]
\centering
\begin{tabular}{p{2.9cm}p{4.8cm}p{4.8cm}}
\toprule
\textbf{Intent} & \textbf{Condition} & \textbf{Action}\\
\midrule
text\_search    & Find specific products         & Search immediately\\
outfit\_request & Request outfit suggestions     & Search + outfit advice\\
follow\_up      & Reference previous result      & Use session context\\
product\_select & Choose numbered items from recent results & Save selected product IDs\\
view\_selections & Ask to review saved picks      & Show selected items list\\
out\_of\_scope  & Unrelated to fashion           & Politely refuse\\
unclear         & Information too vague          & Ask for clarification\\
\bottomrule
\end{tabular}
\caption{Intent classification table with conditions and corresponding actions}
\end{table}

\begin{algorithm}[H]
\caption{LLM-based Intent Classification}\label{alg:intent_class}
\begin{algorithmic}[1]
\Require User query $Q$, Conversation history $H$
\Ensure Classified intent with slots and confidence score
\Function{ClassifyIntent}{$Q, H$}
    \State $H_{text} \gets \text{Format last 4 messages of } H$
    \State $prompt \gets \text{INTENT\_PROMPT}(H_{text}) + Q$
    \State $response \gets \text{LLM.Generate}(prompt)$
    \State $data \gets \text{ParseJSON}(response)$
    \State $intent \gets data.\text{intent} \textbf{ or } \text{``text\_search''}$
    \State $conf \gets data.\text{confidence} \textbf{ or } 0.5$
    \State $slots \gets \text{ExtractSlots}(data)$
    \State \Return $(intent, conf, slots)$
\EndFunction
\end{algorithmic}
\end{algorithm}

\textbf{Explanation:}
\begin{itemize}
    \item \textbf{History-aware}: Uses the last 4 messages to understand context for follow-up queries.
    \item \textbf{Joint extraction}: One call returns intent, coarse filters, six detailed slots, and selected product numbers.
    \item \textbf{Token telemetry}: Prompt and output token counts are attached for logging and cost analysis.
    \item \textbf{Fallback}: On JSON parse error, the classifier defaults to \texttt{text\_search} with confidence 0.5.
\end{itemize}

\section{Step 2 --- Clarification Gate}

\begin{tcolorbox}[title=Method: Rule-Based Slot Readiness \& Hybrid Clarification]
To minimize latency and reduce unnecessary LLM calls, the Clarification Gate utilizes a \textbf{Rule-based Slot Readiness Check} for search intents (\texttt{text\_search}, \texttt{outfit\_request}, \texttt{follow\_up}). It calculates a readiness score based on predefined slot weights and a confidence threshold of $0.75$. For non-search intents or extremely ambiguous queries, it falls back to an LLM-based clarification.
\end{tcolorbox}

\begin{tcolorbox}[colback=green!5,colframe=green!40!black,title=Massive Token \& Latency Optimization]
This architectural change is a \textbf{massive optimization} compared to the previous iteration:
\begin{itemize}
    \item \textbf{Significant Token Savings}: By removing the secondary LLM clarification call, the system saves thousands of input/output tokens per session, drastically reducing API costs.
    \item \textbf{Reduced Latency}: It ensures \textbf{0 LLM calls for most clarifications}. The deterministic templates return instantly, bypassing LLM generation delays.
    \item \textbf{Prevents Useless Searches}: It ensures the search engine (BM25 + Qdrant) is only hit when enough context has been explicitly established, preventing the system from wasting computational resources on broad, noisy searches.
\end{itemize}
\end{tcolorbox}

\subsection{Short-Term Conversation Memory (TTLCache)}
In order to support multi-turn conversations seamlessly, the orchestrator relies on \texttt{TTLCache} (Time-To-Live Cache) to maintain the short-term state of the session in-memory. This acts as a highly optimized conversational state manager, sitting above the long-term PostgreSQL database.

\begin{itemize}
    \item \textbf{\texttt{\_session\_ranked\_slots} (TTL: 1800s)}: This is the most critical cache for the Clarification Gate. As the user talks, extracted entities (like \texttt{color: "red"}) are saved here. If the user's next message is simply ``and for a party,'' the system automatically merges the new \texttt{occasion} slot with the cached \texttt{color} slot. This completely removes the need to constantly re-send the entire chat history back to the LLM to understand the context, drastically saving input tokens.
    \item \textbf{\texttt{\_session\_last\_results} \& \texttt{\_session\_pending\_selection}}: These caches map UI integers (e.g., ``item 1'') back to actual product UUIDs from the most recent search results, allowing the agent to process cart-additions effortlessly.
\end{itemize}

By leveraging \texttt{TTLCache}, the system achieves instant cross-turn entity resolution, avoiding database round-trips and massive token overheads during the iterative search process.

\begin{algorithm}[H]
\caption{Short-Term Memory Management via TTLCache}\label{alg:ttlcache_memory}
\begin{algorithmic}[1]
\Require Current session ID $session\_id$, Newly extracted slots $E_{new}$
\Require Global Cache \texttt{\_session\_ranked\_slots} (TTL=1800s)
\Ensure Updated slots $E_{merged}$ for intent processing
\Function{MergeSessionSlots}{$session\_id, E_{new}$}
    \State $E_{cached} \gets \text{\texttt{\_session\_ranked\_slots}}[session\_id]$ \textbf{or} $\emptyset$
    \State $E_{merged} \gets E_{cached}$
    \For{each $key, value$ in $E_{new}$}
        \If{$value$ is not empty and $value \neq \text{``none''}$}
            \State $E_{merged}[key] \gets value$
        \EndIf
    \EndFor
    \State $\text{\texttt{\_session\_ranked\_slots}}[session\_id] \gets E_{merged}$
    \State \Return $E_{merged}$
\EndFunction
\end{algorithmic}
\end{algorithm}

\subsection{Slot Readiness and Confidence Threshold}
The orchestrator evaluates the accumulated slots against defined weights to determine if the query is ready for execution without prompting the user.

\begin{table}[H]
\centering
\begin{tabular}{lcc}
\toprule
\textbf{Slot} & \textbf{Weight} & \textbf{Requirement}\\
\midrule
Category & 4 & Required for text\_search\\
Color & 3 & Required for text\_search\\
Occasion & 3 & Required for outfit\_request\\
Style & 2 & Secondary signal\\
\bottomrule
\end{tabular}
\caption{Ranked slot weights for readiness scoring}
\end{table}

\begin{algorithm}[H]
\caption{Slot Readiness Evaluation}\label{alg:slot_readiness}
\begin{algorithmic}[1]
\Require Intent string $I$, Dictionary of ranked slots $S$
\Ensure Boolean indicating readiness, List of missing slots
\State $W \gets \{ \text{``category''}: 4, \text{``color''}: 3, \text{``style''}: 2, \text{``occasion''}: 3 \}$
\Function{IsQueryReady}{$I, S$}
    \State $missing \gets \text{CheckMandatorySlots}(I, S)$
    \If{$missing$ is not empty}
        \State \Return $\text{False}, missing$
    \EndIf
    \State $min\_score \gets \text{GetMinScoreForIntent}(I)$ \Comment{e.g., text\_search: 7}
    \State $score \gets 0$
    \For{each $slot, weight$ in $W$}
        \If{$S$ contains valid value for $slot$}
            \State $score \gets score + weight$
        \EndIf
    \EndFor
    \If{$score \ge min\_score$}
        \State \Return $\text{True}, []$
    \Else
        \State \Return $\text{False}, [\text{``one\_of\_four''}]$
    \EndIf
\EndFunction
\end{algorithmic}
\end{algorithm}

\subsection{Deterministic Clarification Questions}
If the query fails the readiness check, or if the intent classification confidence is below the search threshold ($0.75$), the system generates a template-based multilingual clarification question immediately \textbf{without calling the LLM} (0 LLM calls).

\begin{lstlisting}[caption={Deterministic Clarification --- agent/fashion\_agent.py}]
def _resolve_search_query(intent: str, intent_result: ClassifiedIntent, session_id: str, history: list[Message], query: str = "") -> tuple[str, str, "ExtractedSlots"]:
    # ... slot accumulation logic ...
    
    search_confidence_threshold = _get_search_confidence_threshold()
    if intent_result.confidence < search_confidence_threshold:
        low_conf_missing = _readiness_missing_slots(intent, ranked_slots) or ["one_of_four"]
        question = _build_ranked_clarification_question(
            intent, query, low_conf_missing, low_confidence=True
        )
        return "", question, accumulated

    is_ready, missing_slots = _is_query_ready(intent, ranked_slots)
    if not is_ready:
        question = _build_ranked_clarification_question(
            intent, query, missing_slots
        )
        return "", question, accumulated
        
    # Build ranked query...
    return search_query, "", accumulated
\end{lstlisting}

For unclear intents (\texttt{unclear}) or low-confidence non-search intents, the system falls back to the original LLM-based \texttt{check\_clarification} mechanism.

\section{Step 3 --- Memory Agent (PostgreSQL)}

\begin{lstlisting}[caption={Memory Agent --- agent/memory.py}]
def log_query(session_id, query, intent, filters):
    """Record query history to PostgreSQL JSONB."""
    entry = {
        "query": query, "intent": intent,
        "filters": filters, "ts": datetime.utcnow().isoformat()
    }
    with _get_conn() as conn:
        with conn.cursor() as cur:
            cur.execute("""
                UPDATE sessions
                SET query_history = query_history || %s::jsonb
                WHERE session_id = %s
            """, (json.dumps([entry]), session_id))
        conn.commit()

def add_liked_item(session_id, image_id, label, color):
    """Save a product the user has liked."""
    item = {"image_id": image_id,
            "label": label, "color": color}
    with _get_conn() as conn:
        with conn.cursor() as cur:
            cur.execute("""
                UPDATE sessions
                SET liked_items = liked_items || %s::jsonb
                WHERE session_id = %s
            """, (json.dumps([item]), session_id))
        conn.commit()
\end{lstlisting}

\textbf{Explanation:}
\begin{itemize}
    \item \textbf{JSONB append}: Uses PostgreSQL JSONB concatenation (\texttt{||}) to add new entries.
    \item \textbf{Accumulated preferences}: Automatically aggregates preferred categories and colors from history.
    \item \textbf{Limits}: Retains a maximum of 20 query history entries and 50 liked items.
\end{itemize}

\section{Step 4 --- Route \& Execute (Direct Routing)}

\begin{tcolorbox}[title=Method: Deterministic Direct Routing (0 LLM calls)]
Instead of an iterative ReAct loop, the orchestrator uses \textbf{deterministic routing}: intent and slots from Step~1 are forwarded directly to the correct search pipeline. No additional LLM call is needed at this step --- the routing logic is pure Python branching on the classified intent, executing the hybrid search (BM25 + vector + reranker) in one pass.
\end{tcolorbox}

\begin{algorithm}[H]
\caption{Direct Routing Orchestration}\label{alg:routing}
\begin{algorithmic}[1]
\Require User query $Q$, Session $S$
\Ensure Streaming response elements (Events and Results)
\Procedure{OrchestrateStream}{$Q, S$}
    \State \textbf{Yield} ThinkingEvent(``Analyzing...'')
    \State $intent\_res \gets \text{ClassifyIntent}(Q, S.\text{history})$
    \State $intent \gets intent\_res.\text{intent}$
    
    \If{$intent = \text{``out\_of\_scope''}$}
        \State \textbf{Yield} OrchestrateResult(``out\_of\_scope'')
        \State \Return
    \ElsIf{$intent = \text{``product\_select''}$}
        \State \textbf{Yield} HandleProductSelect($\dots$)
        \State \Return
    \EndIf
    
    \State $query, clarify, slots \gets \text{ResolveSearchQuery}(intent, intent\_res)$
    \If{$clarify$ is not empty}
        \State \textbf{Yield} OrchestrateResult(clarification)
        \State \Return
    \EndIf
    
    \State \textbf{Yield} ThinkingEvent(``Searching...'')
    \State $products, reasoning \gets \text{RouteAndExecute}(intent, query, slots)$
    \State \textbf{Yield} OrchestrateResult($products, reasoning$)
\EndProcedure
\end{algorithmic}
\end{algorithm}

\textbf{Fallback Clarification Gate (for unclear non-search intents):}
\begin{lstlisting}[caption={Confidence-based clarification fallback --- agent/fashion\_agent.py}]
# unclear and other non-search intents
if intent_result.confidence < 0.6 or intent == "unclear":
    clarification = check_clarification(
        intent_result.refined_query or "", history=history,
    )
    if clarification.needs_clarification:
        return "", clarification.question, ExtractedSlots()
\end{lstlisting}

\textbf{Routing decisions:}
\begin{itemize}
    \item \texttt{out\_of\_scope} --- Return polite refusal immediately (0 LLM)
    \item \texttt{product\_select} --- Save selected product IDs, offer confirmation (0 LLM)
    \item \texttt{view\_selections} --- Return saved picks from session (0 LLM)
    \item \texttt{text\_search} / \texttt{outfit\_request} / \texttt{follow\_up} --- Run hybrid search pipeline
    \item Confidence $< 0.6$ or \texttt{unclear} --- Fire clarification gate
\end{itemize}

\section{Step 5 --- Gender Filtering and LLM Synthesis}

Before finalizing the results, the system applies demographic-aware post-processing. A specific \texttt{\_filter\_by\_gender} function validates the retrieved products against the user's recorded gender in PostgreSQL, ensuring that (for example) female-specific clothing is not inappropriately recommended to male users.

\begin{lstlisting}[caption={LLM Synthesis --- agent/fashion\_agent.py}]
def _synthesize_response(
    query: str,
    products: list[NodeWithScore],
    history: list[Message],
    intent: str,
    client: LLMClient,
    preferences: Optional[dict] = None,
    session_id: Optional[str] = None,
) -> tuple[str, str]:
    """Use Gemini/GPT/Claude to synthesize a natural response."""
    ctx = _build_synthesis_context(
        query, products, history, preferences, session_id)
    prompt = SYNTHESIS_PROMPT.format(query=query, **ctx)
    try:
        response_text = client.generate(prompt)
        data = parse_llm_json(response_text)
        return data.get("answer", ""), data.get("styling_suggestion", "")
    except Exception:
        return fallback_text_response(products), ""
\end{lstlisting}

\textbf{Explanation:}
\begin{itemize}
    \item \textbf{Gender Context Injection}: By explicitly stating the \texttt{gender\_context} in the prompt, Gemini can tailor the phrasing and styling tips appropriately (e.g., suggesting a ``sharp tailored fit'' for men vs. a ``flattering silhouette'' for women).
\end{itemize}

% ===========================================================================
% CHAPTER 6: AGENT v2.0 --- PATH 2: IMAGE-TO-IMAGE SEARCH
% ===========================================================================
