% Chapter 8: CONCLUSION
% Content from: evaluation_conclusion.tex (lines 144-191)

\section{Conclusion}
This project successfully built an intelligent multimodal fashion search system following a clear two-phase roadmap. The RAG v1.0 phase established a hybrid search foundation with FashionCLIP 2.0 and BM25, while Agent v2.0 PATH 1 upgraded to a proactive architecture featuring a ReAct loop, intent classification, a clarification gate, and persistent memory via PostgreSQL.

Version v2.0 represents significant improvements over v1.0:
\begin{itemize}
    \item \textbf{Embedding}: Upgraded from FashionCLIP (512-d) to Marqo-FashionSigLIP (768-d).
    \item \textbf{Query Expansion}: Added Gemini-powered synonym expansion for short queries.
    \item \textbf{Reranker}: Integrated BGE Reranker v2-m3 cross-encoder for improved precision.
    \item \textbf{Deployment}: Docker Compose stack with 4 services (PostgreSQL + Qdrant + FastAPI + Cloudflare Tunnel).
\end{itemize}

\subsection{Evidence-Based Claim Mapping for Final Conclusion}
\label{subsec:evidence_claim_mapping}

Final claims are mapped to evidence strength so that conclusions remain proportional to verified data:

\begin{table}[H]
\centering
\begin{tabular}{p{4.0cm}p{5.8cm}p{3.0cm}}
\toprule
\textbf{Claim} & \textbf{Primary Evidence} & \textbf{Status}\\
\midrule
Agent v2.0 improves retrieval quality over v1.0. & Recall@5, MRR, Hit Rate@5 (Section~\ref{sec:data_evidence_integrity} and Section~\ref{subsec:metric_definitions_boundaries}). & Supported\\
Agent behavior is robust in multi-turn interaction. & Task completion, faithfulness, and clarification behavior logs. & Supported\\
Operational LLM cost is explainable and monitorable. & \texttt{llm\_token\_usage}, \texttt{session\_token\_summary}, mode cost aggregation. & Partially supported\\
User purchase tendency is improved by recommendations. & CartAddRate / WillBuyRate / ConversionRate from behavior funnel. & Inconclusive (depends on cohort size and balance)\\
\bottomrule
\end{tabular}
\caption{Claim-to-evidence mapping used in the final thesis conclusion}
\label{tab:claim_evidence_mapping}
\end{table}

Therefore, the final conclusion follows three rules: (1) only claims marked \textit{Supported} are stated as confirmed findings, (2) \textit{Partially supported} claims are reported with operational caveats, and (3) \textit{Inconclusive} claims are retained as hypotheses for future data collection.

\textbf{Current evidence limitations.}
\begin{itemize}
    \item Token-to-cost estimates depend on fixed public list prices and may vary over time.
    \item Behavior metrics are sensitive to sample imbalance across orchestration modes and user groups.
    \item Conversion-style claims require larger longitudinal cohorts than early-stage thesis collection windows.
\end{itemize}

\textbf{Future development directions:}
\begin{itemize}
    \item \textbf{Phase 3}: Scale dataset to 15K--100K products, fine-tune the reranker, Redis session cache.
    \item \textbf{Phase 4}: Virtual Try-on (IDM-VTON), fine-tune FashionSigLIP on proprietary data, A/B testing.
    \item \textbf{PATH 2}: Image-to-Image search with Composed Search.
\end{itemize}
